Generating and modifying matrices

### 2016-12-20 Analysis/Character_difference/Modifying_matrices.Rmd
Modifying vignettes for new compilation

```{r, results="hide", message=FALSE}
library(Claddis) ; library(dispRity) ; library(diversitree)
source("functions.R") ; load.functions(test = FALSE)

## Load the C libraries
dyn.load("../Functions/char.diff.so")

>>>>

```{r, results="hide", message=FALSE}
library(Claddis) ; library(dispRity) ; library(diversitree)
source("../../Functions/cor.matrix.R")
source("../../Functions/modify.matrix.R")
source("../../Functions/plot.char.diff.density.R")
source("../../Functions/plot.cor.matrix.R")
source("../../Functions/write.nexus.std.R")
source("../../Functions/char.diff.R")

## Load the C libraries
dyn.load("../../Functions/char.diff.so")
